New insights into the Weddell Sea ecosystem applying a network approach

### 2022-08-19 Manuscript/Manuscript.Rmd
Re-estimations phytodetritus & sediment

With the aim of studying the relationship between the interaction strength of the species and its unweighted properties, we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties. The statistical significance of the fitted slopes was tested, as well as the difference between the groups' slopes applying least-squares means [@Harvey1960].

@@

\textbf{Model} & \textbf{df} & \textbf{AIC} & \textbf{deltaAIC} \\
\middlehline
log-Normal & 2 & -356579 & 0 \\
\middlehline
Gamma & 2 & -352575 & 4004 \\
\middlehline
Power-law & 2 & -347646 & 8933 \\
\middlehline
Exponential & 1 & -262852 & 93726 \\
\middlehline
Normal & 2 & -222785 & 133793 \\
\middlehline
Uniform & 2 & -178001 & 178578 \\

@@

\textbf{Species} & \textbf{meanIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{StabDif} & \textbf{ADvalue}\\
\middlehline
Orcinus orca & 0.00163 & 5.03 & 26 & 0.037 & Benthopelagic & 0.00040 & 1.38e-51 \\
\middlehline
Macrourus holotrachys & 0.00074 & 4.70 & 85 & 0.112 & Benthopelagic & 0.00027 & 2.75e-18 \\
\middlehline
Abyssorchomene nodimanus & 0.00022 & 4.21 & 137 & 0.130 & Benthopelagic & 0.00024 & 1.02e-15 \\
\middlehline
Dissostichus mawsoni & 0.00069 & 4.12 & 87 & 0.126 & Pelagic & 0.00018 & 1.06e-10 \\
\middlehline
Pagetopsis macropterus & 0.00063 & 4.64 & 76 & 0.113 & Demersal & -0.00017 & 1.66e- 9 \\
\middlehline
Macrourus whitsoni & 0.00064 & 4.55 & 92 & 0.124 & Benthopelagic & 0.00012 & 4.97e- 8 \\
\middlehline
Hydrurga leptonyx & 0.00092 & 4.72 & 67 & 0.094 & Land-based & 0.00014 & 5.59e- 6 \\
\middlehline
Mesonychoteuthis hamiltoni & 0.00161 & 4.41 & 29 & 0.028 & Pelagic & 0.00013 & 6.53e- 6 \\
\middlehline
Notothenia marmorata & 0.00073 & 4.09 & 44 & 0.091 & Demersal & 0.00014 & 2.10e- 5 \\
\middlehline
Champsocephalus gunnari & 0.00068 & 3.72 & 46 & 0.086 & Pelagic & 0.00010 & 7.97e- 5 \\
\middlehline
Arctocephalus gazella & 0.00083 & 4.67 & 61 & 0.093 & Land-based & 0.00011 & 9.52e- 5 \\
\middlehline
Ommatophoca rossii & 0.00093 & 4.87 & 56 & 0.080 & Land-based & 0.00009 & 1.20e- 3 \\
\middlehline
Notothenia coriiceps & 0.00044 & 4.27 & 130 & 0.126 & Demersal & 0.00012 & 1.33e- 3 \\

>>>>

Furthermore, we took into account the species' habitat, which describes the physical position of a species within the environment. These data was taken from @Jacob2011. The species were categorized as: 1) benthic, if the species lives on the seafloor; 2) pelagic, if the species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not aquatic but feeds predominantly in the marine realm.

With the aim of studying the relationship between the interaction strength of the species and its unweighted properties and habitat, we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties. The statistical significance of the fitted slopes was tested, as well as the difference between the groups' slopes applying least-squares means [@Harvey1960].

@@

\textbf{Model} & \textbf{df} & \textbf{AIC} & \textbf{deltaAIC} \\
\middlehline
log-Normal & 2 & -358648 & 0 \\
\middlehline
Gamma & 2 & -354821 & 3827 \\
\middlehline
Power-law & 2 & -349999 & 8649 \\
\middlehline
Exponential & 1 & -262855 & 95793 \\
\middlehline
Normal & 2 & -222785 & 135863 \\
\middlehline
Uniform & 2 & -178001 & 180647 \\

@@

\textbf{Species} & \textbf{meanIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{StabDif} & \textbf{ADvalue}\\
\middlehline
Orcinus orca & 0.00163 & 5.03 & 26 & 0.037 & Benthopelagic & 0.00040 & 1.89e-63 \\
\middlehline
Macrourus holotrachys & 0.00074 & 4.70 & 85 & 0.112 & Benthopelagic & 0.00027 & 1.86e-21 \\
\middlehline
Abyssorchomene nodimanus & 0.00022 & 4.21 & 137 & 0.130 & Benthopelagic & 0.00023 & 2.64e-16 \\
\middlehline
Dissostichus mawsoni & 0.00069 & 4.12 & 87 & 0.126 & Pelagic & 0.00020 & 1.74e-11 \\
\middlehline
Macrourus whitsoni & 0.00064 & 4.55 & 92 & 0.124 & Benthopelagic & 0.00015 & 3.98e- 9 \\
\middlehline
Notothenia marmorata & 0.00074 & 4.09 & 44 & 0.091 & Demersal & 0.00016 & 1.90e- 7 \\
\middlehline
Pagetopsis macropterus & 0.00063 & 4.64 & 76 & 0.113 & Demersal & -0.00014 & 6.64e- 7 \\
\middlehline
Champsocephalus gunnari & 0.00068 & 3.72 & 46 & 0.086 & Pelagic & 0.00017 & 1.33e- 6 \\
\middlehline
Notothenia coriiceps & 0.00044 & 4.27 & 130 & 0.126 & Demersal & 0.00012 & 2.45e- 6 \\
\middlehline
Hydrurga leptonyx & 0.00092 & 4.72 & 67 & 0.094 & Land-based & 0.00013 & 4.15e- 6 \\
\middlehline
Mesonychoteuthis hamiltoni & 0.00161 & 4.41 & 29 & 0.028 & Pelagic & 0.00013 & 2.99e- 5 \\
\middlehline
Arctocephalus gazella & 0.00083 & 4.67 & 61 & 0.093 & Land-based & 0.00014 & 5.14e- 5 \\
\middlehline
Gonatus antarcticus & 0.00080 & 4.31 & 36 & 0.046 & Pelagic & 0.00012 & 5.90e- 4 \\
\middlehline
Psychroteuthis glacialis & 0.00047 & 3.91 & 23 & 0.054 & Pelagic & 0.00011 & 1.66e- 3 \\
\middlehline
Mirounga leonina & 0.00107 & 4.87 & 56 & 0.080 & Land-based & 0.00009 & 3.50e- 3 \\
\middlehline
Dacodraco hunteri & 0.00064 & 4.80 & 65 & 0.101 & Demersal & 0.00006 & 7.51e- 3 \\

### 2022-08-19 Manuscript/Manuscript.tex
Re-estimations phytodetritus & sediment

We obtained estimations for the resource density and the search rate
from the scaling relationships with the resource and the consumer mass,
respectively \citep{Pawar2012}. The coefficients of such relationships,
determined by ordinary least squares regression, vary with the
interaction dimensionality. On one hand, resource density scales with
resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in
2D and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources
`detritus' and `sediment' were not available in GATEWAy, we estimated it
considering the scaling relationship with consumer mass, also different
in 2D and 3D (for details see equation S9 and figures 2c-d of
Supplementary Information in \citet{Pawar2012}). On the other hand,
search rate scales with consumer mass as a power-law with exponents
\vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.

@@

With the aim of studying the relationship between the interaction
strength of the species and its unweighted properties, we performed
linear regression analyses between the log(mean interaction strength)
and each of the mentioned unweighted properties. The statistical
significance of the fitted slopes was tested, as well as the difference
between the groups' slopes applying least-squares means
\citep{Harvey1960}.

>>>>

We obtained estimations for the resource density and the search rate
from the scaling relationships with the resource and the consumer mass,
respectively \citep{Pawar2012}. The coefficients of such relationships,
determined by ordinary least squares regression, vary with the
interaction dimensionality. On one hand, resource density scales with
resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in
2D and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources
`phytodetritus' and `sediment' were not available in GATEWAy, we
considered the body mass of the smallest phytoplankton species
(`Fragilariopsis cylindrus') as a proxy. This is justified by the fact
that `phytodetritus' and `sediment' are mainly composed by dead or
senescent phytoplankton reaching the seabed (\citet{Wolanski2011}). On
the other hand, search rate scales with consumer mass as a power-law
with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08}
in 3D.

@@

Furthermore, we took into account the species' habitat, which describes
the physical position of a species within the environment. These data
was taken from \citet{Jacob2011}. The species were categorized as: 1)
benthic, if the species lives on the seafloor; 2) pelagic, if the
species lives close to the surface; 3) benthopelagic, if it moves
between and connects the mentioned environments; 4) demersal, lives and
feeds on or near the bottom of the sea; and 5) land-based, if the
consumer is not aquatic but feeds predominantly in the marine realm.

With the aim of studying the relationship between the interaction
strength of the species and its unweighted properties and habitat, we
performed linear regression analyses between the log(mean interaction
strength) and each of the mentioned unweighted properties. The
statistical significance of the fitted slopes was tested, as well as the
difference between the groups' slopes applying least-squares means
\citep{Harvey1960}.
